---
title: "Master Seminar Paper Intermediary Asset Pricing"
author: "Janik Müller"
format: html
date: today
toc: true
---

# 0 Synopsis
We will use this document to write our seminar paper. We will use the `quarto` package to write the paper in a literate programming style. This means that we will write the paper in a single document that includes both the content and the code used to generate the content. This will allow us to easily reproduce the results in the paper. Furthermore, we will submit a separate pdf file that only includes the text without the need to run the code. Moreover, we will use the `quarto` package to generate the pdf file where the code is hidden. 

```{r echo=FALSE, warning=FALSE, message=FALSE}
source("scripts/packages.R")
source("scripts/functions.R")
```


# 1 Introduction

In this paper, we will investigate the intermediary asset pricing model proposed by Sa Mai (2023) where a semi parametric approach was used in to model the heterogeneous intermediary stochastic discount factor (HI-SDF).

# 2 Data

First, let us check the data that we have available for our analysis. 


## 2.1 Data Import

```{r message=FALSE, eval=TRUE, output=FALSE}
# Import all data files
process_data_directory(data_dir = data_dir)
```

```{r echo = FALSE}
# print(paste("Successfully Loaded:", ls()))
```


## 2.2 Data Cleaning

### 2.2.1 Broker Dealer (BD) - Leverage Ratio

For the broker dealers we are going to use the total financial assets and liabilities to calculate the leverage ratio.

```{r warning=FALSE, message=FALSE}
### Assets
# Extract Total Assets and Total Liabilities and Equity for Broker Dealers
total_assets_bd <- df_L.130 %>% filter(`Descriptions:` == "Security brokers and dealers; total financial assets")

# Select the columns
total_assets_bd <- total_assets_bd %>% 
    dplyr::select(-"Descriptions:", -"Unit:", -"Currency:", -"Unique Identifier:", -"Series Name:", -"Multiplier:")

# Replace ND with NA
total_assets_bd <- total_assets_bd %>% 
    mutate(across(everything(),
                  ~ as.numeric(.)
                  )
           )

# Total Assets into long format
total_assets_bd_long <- total_assets_bd %>%
    pivot_longer(
        cols = everything(),
        names_to = "Quarter",
        values_to = "Value"
    ) %>% 
    filter(Quarter >= "1970 Q1")


### Liabilities

# Extract Total Liabilities and Equity for Broker Dealers
total_liabilities_bd <- df_L.130 %>% filter(`Descriptions:` == "Security brokers and dealers; total liabilities")

# Select the columns
total_liabilities_bd <- total_liabilities_bd %>% 
    dplyr::select(-"Descriptions:", -"Unit:", -"Currency:", -"Unique Identifier:", -"Series Name:", -"Multiplier:")

# Replace ND with NA
total_liabilities_bd <- total_liabilities_bd %>% 
    mutate(across(everything(),
                  ~ as.numeric(.)
                  )
           )



# Total Liabilities into long format
total_liabilities_bd_long <- total_liabilities_bd %>%
    pivot_longer(
        cols = everything(),
        names_to = "Quarter",
        values_to = "Value"
    ) %>% 
    filter(Quarter >= "1970 Q1")


# Calculate the leverage ratio
leverage_ratio_bd <- total_assets_bd / (total_assets_bd - total_liabilities_bd)

rm(df_L.130)
```

<br>

Plot of the Log-Leverage of Broker Dealers:

```{r, echo=FALSE}
# Bring into the Long format
leverage_ratio_bd_long <- leverage_ratio_bd %>%
    pivot_longer(
        cols = everything(),
        names_to = "Quarter",
        values_to = "Value"
    )
leverage_ratio_bd_long <- leverage_ratio_bd_long %>% 
    mutate(Quarter = as.yearqtr(Quarter, format = "%YQ%q")) %>%
    filter(Quarter >= "1970 Q1")



# Plot of Broker Dealers Log-Leverage Ratio
leverage_ratio_bd_long %>% 
    ggplot(aes(x = Quarter, y = log(Value))) +
    geom_line() +
    labs(title = "Log-Leverage Ratio of Broker Dealers",
         x = "Quarter",
         y = "Log-Leverage Ratio") +
    theme_minimal()
```






### 2.2.2 Bank Holding Company (BHC) - Leverage Ratio

For the bank holding companies we are going to use the total financial assets and liabilities to calculate the leverage ratio. 

```{r warning=FALSE, message=FALSE}
# Extract Total Assets and Total Liabilities and Equity for Bank Holding Companies
total_assets_bhc <- df_L.131 %>% filter(`Descriptions:` == "Holding companies; total financial assets")

# Select the columns
total_assets_bhc <- total_assets_bhc %>% 
    dplyr::select(-"Descriptions:", -"Unit:", -"Currency:", -"Unique Identifier:", -"Series Name:", -"Multiplier:")

# Replace ND with NA
total_assets_bhc <- total_assets_bhc %>% 
    mutate(across(everything(),
                  ~ as.numeric(.)
                  )
           )


# Extract Total Liabilities and Equity for Bank Holding Companies
total_liabilities_bhc <- df_L.131 %>% filter(`Descriptions:` == "Holding companies; total liabilities")

# Select the columns
total_liabilities_bhc <- total_liabilities_bhc %>% 
    dplyr::select(-"Descriptions:", -"Unit:", -"Currency:", -"Unique Identifier:", -"Series Name:", -"Multiplier:")

# Replace ND with NA
total_liabilities_bhc <- total_liabilities_bhc %>% 
    mutate(across(everything(),
                  ~ as.numeric(.)
                  )
           )





# Calculate the leverage ratio
leverage_ratio_bhc <- total_assets_bhc / (total_assets_bhc - total_liabilities_bhc)

rm(df_L.131)
```




<br>

Plot of the Log-Leverage of Bank Holding Companies:

```{r, echo=FALSE}
# Bring into the Long format
leverage_ratio_bhc_long <- leverage_ratio_bhc %>%
    pivot_longer(
        cols = everything(),
        names_to = "Quarter",
        values_to = "Value"
    )

leverage_ratio_bhc_long <- leverage_ratio_bhc_long %>%
    mutate(Quarter = as.yearqtr(Quarter, format = "%YQ%q")) %>%
    filter(Quarter >= "1970 Q1")

# Plot of Bank Holding Companies Log-Leverage Ratio
leverage_ratio_bhc_long %>% 
    ggplot(aes(x = Quarter, y = log(Value))) +
    geom_line() +
    labs(title = "Log-Leverage Ratio of Bank Holding Companies",
         x = "Quarter",
         y = "Log-Leverage Ratio") +
    theme_minimal()
```

<br>


### 2.2.3 Aggregate Leverage Ratio

We will calculate the aggregate leverage ratio for the broker dealers and bank holding companies. 
Defined as total assets BD and BHC over total equity.

```{r warning=FALSE, message=FALSE}
# Calculate the aggregate leverage ratio
aggregate_leverage <- (total_assets_bd + total_assets_bhc) / (total_assets_bd + total_assets_bhc - total_liabilities_bd - total_liabilities_bhc)
```

<br>

Plot the aggregate Leverage Ratio:

```{r, echo=FALSE}
# Bring into the Long format
aggregate_leverage_long <- aggregate_leverage %>%
    pivot_longer(
        cols = everything(),
        names_to = "Quarter",
        values_to = "Value"
    )

aggregate_leverage_long <- aggregate_leverage_long %>%
    mutate(Quarter = as.yearqtr(Quarter, format = "%YQ%q")) %>%
    mutate(Quarter = Quarter - 0.25) %>%
    filter(Quarter >= "1970 Q1")

# Plot of Aggregate Leverage Ratio
aggregate_leverage_long %>% 
    ggplot(aes(x = Quarter, y = log(Value))) +
    geom_line() +
    labs(title = "Log-Aggregate Leverage Ratio of Broker Dealers and Bank Holding Companies",
         x = "Quarter",
         y = "Log-Aggregate Leverage Ratio") +
    theme_minimal()
```


### 2.2.4 Net Worth Share Calculation

We will calculate the net worth share for the broker dealers and bank holding companies. 

```{r warning=FALSE, message=FALSE}
# Calculate the Net Worth Share
net_worth_share <- (total_assets_bhc - total_liabilities_bhc) / ((total_assets_bhc + total_assets_bd) - (total_liabilities_bhc + total_liabilities_bd))
```

Plot of the net worth share:

```{r, echo=FALSE}
# Bring into the Long format

net_worth_share_long <- net_worth_share %>%
    pivot_longer(
        cols = everything(),
        names_to = "Quarter",
        values_to = "Value"
    )

net_worth_share_long <- net_worth_share_long %>%
    mutate(Quarter = as.yearqtr(Quarter, format = "%YQ%q")) %>%
    mutate(Quarter = Quarter - 0.25) %>%
    filter(Quarter >= "1970 Q1")

# Plot of Net Worth Share
net_worth_share_long %>% 
    ggplot(aes(x = Quarter, y = Value)) +
    geom_line() +
    labs(title = "Net Worth Share of Broker Dealers and Bank Holding Companies",
         x = "Quarter",
         y = "Net Worth Share") +
    theme_minimal()
```






#### PLots for the seminar paper

Here we will make plots of log leverage together for bd and bhc.

```{r}
# Merge the dataframes
leverage_ratio_full_table <- leverage_ratio_bd_long %>% 
    inner_join(leverage_ratio_bhc_long, by = c("Quarter")) %>%
    rename(bd = Value.x, bhc = Value.y) %>% 
    mutate(bd = log(bd) , bhc = log(bhc)) 

leverage_ratio_plot <- leverage_ratio_full_table %>%
    mutate(Institution = ifelse(Institution == "bd", "Broker Dealers", "Bank Holding Companies")) %>%
    pivot_longer(
        cols = c(bd, bhc),
        names_to = "Institution",
        values_to = "Value"
    ) 

# Plot the data


leverage_ratio_plot %>% 
    ggplot(aes(x = Quarter, y = Value, color = Institution)) +
    geom_line() +
    # Put the values on different axes to make them better comparable
    facet_wrap(~Institution, scales = "free_y") +
    labs(title = "Log-Leverage Ratio of Broker Dealers and Bank Holding Companies",
         x = "Quarter",
         y = "Log-Leverage Ratio") +
    theme_bw() +
    theme(legend.position = "", 
          axis.text.x = element_text(angle = 45, hjust = 1), 
           plot.title = element_text(hjust = 0.5, face = "bold"))

df_GDP <- df_GDP %>% 
    mutate(Quarter = as.yearqtr(observation_date, format = "%Y-%m-%d")) %>%
    dplyr::select(-DATE, GDP = GDP) %>% 
    filter(Quarter >= "1970 Q4")


# Calculate the correlation between innovation of GDP and Residual of an AR(1) process between levergage and GDP
leverage_ratio_full_table <- df_GDP%>% 
    inner_join(leverage_ratio_full_table) 

# Calcualte ar1
ar1_bd <- arima(leverage_ratio_full_table$bd, order = c(1,0,0))
ar1_bhc <- arima(leverage_ratio_full_table$bhc, order = c(1,0,0))

# Calculate the residuals
residuals_bd <- residuals(ar1_bd)
residuals_bhc <- residuals(ar1_bhc)

leverage_ratio_full_table <- leverage_ratio_full_table %>% 
    mutate(residuals_bd = residuals_bd, residuals_bhc = residuals_bhc)


# Calculate the correlation
correlation_bd_bhc <- cor(leverage_ratio_full_table$residuals_bd, leverage_ratio_full_table$residuals_bhc)

# Calculate the innovation of gdp
leverage_ratio_full_table <- leverage_ratio_full_table %>% 
    mutate(GDP_innovation = lead(GDP) / GDP) %>%
    slice(1:n()-1, )

correlation_bd_gdp <- cor(leverage_ratio_full_table$residuals_bd, leverage_ratio_full_table$GDP_innovation)
correlation_bhc_gdp <- cor(leverage_ratio_full_table$residuals_bhc, leverage_ratio_full_table$GDP_innovation)

```





```{r}

networth_share_full_table <- net_worth_share_long %>% 
    inner_join(aggregate_leverage_long, by = c("Quarter")) %>%
    rename("Net Worth Share" = Value.x, "Aggregate Leverage" = Value.y)

networth_share_full_table_long <- networth_share_full_table %>% 
    pivot_longer(
        cols = c("Net Worth Share", "Aggregate Leverage"),
        names_to = "Institution",
        values_to = "Value"
    )


# Plot the data
networth_share_full_table_long %>% 
    ggplot(aes(x = Quarter, y = Value, color = Institution)) +
    geom_line() +
    # Put the values on different axes to make them better comparable
    facet_wrap(~Institution, scales = "free_y") +
    labs(title = "Net Worth Share and Aggregate Leverage Ratio of Broker Dealers and Bank Holding Companies",
         x = "Quarter",
         y = "Value") +
    theme_bw() +
    theme(legend.position = "", 
          axis.text.x = element_text(angle = 45, hjust = 1), 
           plot.title = element_text(hjust = 0.5, face = "bold"))
```














### 2.2.5 Personal Expenditure - Consumption Growth

We will calculate the consumption growth rate for the personal expenditure data. 

```{r}
# Calculate the consumption growth rate
df_pce_growth <- df_PCECC96 %>% 
    mutate(Quarter = as.yearqtr(DATE, format = "%Y-%m-%d")) %>%
    dplyr::select(-DATE, PCE = PCECC96) %>% 
    mutate(pce_growth = lead(PCE) / PCE) %>% 
    filter(Quarter >= "1970 Q4") %>%
    filter(row_number() != n())
```


Now we will plot the consumption growth rate:

```{r, echo=FALSE}
# Plot of Consumption Growth Rate
df_pce_growth %>% 
    ggplot(aes(x = Quarter, y = pce_growth)) +
    geom_line() +
    labs(title = "Personal Consumption Expenditure Growth Rate",
         x = "Quarter",
         y = "Growth Rate") +
    theme_minimal()
```


### 2.2.6 Historical Return Data

We will calculate the historical return data for equity, non-equity, risk-free (i.e. treasury bill), commodities, CDS, options and FX data, as well as a combined portfolio. 


#### 1 Equity Portfolios

```{r}
## Equity Portfolios

# List the Dataframes
list_of_dataframes <- c(
    "df_10_Portfolios_Prior_60_13",
    "df_25_Portfolios_5x5",
    "df_25_Portfolios_ME_INV_5x5",
    "df_25_Portfolios_ME_OP_5x5"
)




# Change dataframes to date format
for (dataframe_name in list_of_dataframes) {
    # Retrieve the dataframe by name
    dataframe <- get(dataframe_name)
    # Apply the function
    modified_dataframe <- change_to_date(dataframe)
    # Assign the modified dataframe back to its original name
    assign(dataframe_name, modified_dataframe)
    # Remove the modified dataframe from the environment
    rm(modified_dataframe)
}


# Merge dataframes in the list of dataframes on date column
df_equity_monthly <- df_10_Portfolios_Prior_60_13 %>% 
    inner_join(df_25_Portfolios_5x5, by = "date") %>% 
    inner_join(df_25_Portfolios_ME_INV_5x5, by = "date") %>% 
    inner_join(df_25_Portfolios_ME_OP_5x5, by = "date")

# Make Returns decimal number
df_equity_monthly <- df_equity_monthly %>% 
    mutate(across(-date, ~ . / 100))

# Turn monthly returns into quarterly gross returns
df_equity_monthly <- df_equity_monthly %>% 
    mutate(Quarter = as.yearqtr(date, format = "%Y-%m-%d")) %>% 
    group_by(Quarter) %>%
    summarise(across(-date, ~ prod(1 + .)))

# Put into long Format with asset_id and asset_class
df_equity_monthly_long <- df_equity_monthly %>%
    pivot_longer(
        cols = -Quarter,
        names_to = "portfolio_id",
        values_to = "returns"
    )

# Include equity asset class
df_equity_monthly_long <- df_equity_monthly_long %>% 
    mutate(asset_class = "equity")


# Include specific asset_id
df_equity <- df_equity_monthly_long %>%
  mutate(asset_id = case_when(
    grepl("^Lo PRIOR|^PRIOR [2-9]$", portfolio_id) ~ "long_run_reversals",
    grepl("^Hi PRIOR$", portfolio_id) ~ "long_run_reversals",
    grepl("^SMALL LoBM|^ME[1-5] BM[1-5]|^BIG LoBM$", portfolio_id) ~ "size_bm",
    grepl("^SMALL HiBM|^BIG HiBM$", portfolio_id) ~ "size_bm",
    grepl("^SMALL LoINV|^ME[1-5] INV[1-5]|^BIG LoINV$", portfolio_id) ~ "size_inv",
    grepl("^SMALL HiINV|^BIG HiINV$", portfolio_id) ~ "size_inv",
    grepl("^SMALL LoOP|^ME[1-5] OP[1-5]|^BIG LoOP$", portfolio_id) ~ "size_op",
    grepl("^SMALL HiOP|^BIG HiOP$", portfolio_id) ~ "size_op",
    TRUE ~ "unknown"  # Default category if no match is found
  ))

# Make returns to t+1 returns
df_equity <- df_equity %>% mutate(Quarter = Quarter - 0.25)

# Remove unnecessary dataframes
rm(list_of_dataframes)
rm(df_10_Portfolios_Prior_60_13)
rm(df_25_Portfolios_5x5)
rm(df_25_Portfolios_ME_INV_5x5)
rm(df_25_Portfolios_ME_OP_5x5)
rm(dataframe)
```


#### 2 Non-Equity Portfolios

Here we will clean in the He, Kelly and Manela data for non-equity portfolios. 


```{r}
# Subset non-equity data
non_equity_HKM <- df_He_Kelly_Manela_Factors_And_Test_Assets[, c(1, 37:ncol(df_He_Kelly_Manela_Factors_And_Test_Assets))]

# Make first column to yearqtr
non_equity_HKM <- non_equity_HKM %>%
    mutate(yyyyq = as.yearqtr(as.character(yyyyq), format = "%Y%q")) %>% 
    rename(Quarter = yyyyq)


# Make the Returns to gross returns
non_equity_HKM <- non_equity_HKM %>% 
    mutate(across(-Quarter, ~ . + 1))

# Add asset class
non_equity_HKM <- non_equity_HKM %>% 
    pivot_longer(
        cols = -Quarter,
        names_to = "portfolio_id",
        values_to = "returns"
    ) %>% 
    mutate(asset_class = "non_equity")

# Add asset_id
non_equity_HKM <- non_equity_HKM %>%
  mutate(asset_id = case_when(
    grepl("^US_bonds_", portfolio_id) ~ "government_bonds",
    grepl("^Sov_bonds_", portfolio_id) ~ "sovereign_bonds",
    grepl("^Options_", portfolio_id) ~ "options",
    grepl("^CDS_", portfolio_id) ~ "credit_default_swaps",
    grepl("^Commod_", portfolio_id) ~ "commodities",
    grepl("^FX_", portfolio_id) ~ "foreign_exchange",
    grepl("^All_", portfolio_id) ~ "all",
    TRUE ~ "unknown"  # Default category if no match is found
  ))


# Remove all assets called "all"
non_equity_HKM <- non_equity_HKM %>% 
    filter(asset_id != "all") %>%
    mutate(Quarter = Quarter - 0.25)
```



#### 3 Risk-Free Rate

```{r}
# Extract the risk-free rate
r_f <- df_TB3MS
#rm(df_TB3MS)

# Change date to yearqtr
r_f <- r_f %>% 
    mutate(Quarter = as.yearqtr(observation_date, format = "%Y-%m-%d")) %>% 
    dplyr::select(-observation_date) %>%
    rename(returns = TB3MS)

# Divide the rf by 100 to get the decimal number
r_f <- r_f %>% 
    mutate(returns = returns / 100)

# Calculate Quarterly r_f
r_f <- r_f %>% 
    group_by(Quarter) %>%
    summarise(returns = prod(1 + returns))


# Add asset class
r_f <- r_f %>% 
    mutate(asset_class = "risk_free_rate", asset_id = "risk_free_rate") %>%
    mutate(Quarter = Quarter - 0.25)
```


#### 4 Instruments

##### 1 CAY

```{r}
# Change date to yearqtr
df_cay_current <- df_cay_current %>% 
    mutate(Quarter = as.yearqtr(date, format = "%Y-%m-%d")) %>% 
    dplyr::select(-date) %>%
    rename(cay_t = `cay=c-0.218 a-0.801y+0.441`)

```


1. Wealth


```{r}

# Add the necessary data till 2024

start_year_qtr <- as.Date("2019-12-01")
end_year_qtr <- as.Date("2024-09-01")    
yq <- seq(as.yearqtr(start_year_qtr), as.yearqtr(end_year_qtr), by = 1/4)


# Wealth data

# Remove unnecessary columns
df_wealth <- df_wealth[c(1,20), -c(1:6)]

# Calculate net wealth of households
df_wealth_net <- df_wealth[1, ] - df_wealth[2, ]

# Wealth data into long format
df_wealth_net_long <- df_wealth_net %>%
    pivot_longer(
        cols = everything(),
        names_to = "Quarter",
        values_to = "Value"
    )

# Change wealth into log scale
df_wealth_net_long <- df_wealth_net_long %>% 
    mutate(Value = log(Value))

# Calculate growth rate of df_wealth_net_long
df_wealth_growth <- df_wealth_net_long %>% 
    mutate(Quarter = as.yearqtr(Quarter, format = "%YQ%q")) %>% 
    mutate(wealth_growth = log(Value / df_wealth_net_long$Value[3])) %>%
    slice(4:n())

# Use growth rate to calculate the wealth growth until 2024
growth_rate_wealth <-  df_wealth_growth$wealth_growth
additional_wealth <- df_cay_current$w[nrow(df_cay_current)] * exp(growth_rate_wealth)



# Add the additional wealth to the cay data
df_cay_current <- df_cay_current %>% 
    add_row(Quarter = yq, 
            w = additional_wealth)

```



2. Labor Income

```{r}
# Labor Income


df_labor_income <- df_labor_income[2, -c(1:2)]

# Bring into long format
df_labor_income_long <- df_labor_income %>%
  pivot_longer(
    cols = everything(),  
    names_to = "Year",  
    values_to = "Value"
  ) %>% 
    mutate(Year = as.numeric(Year))


# Intrapolate the labor income data to quarterly data
df_labor_income_long <- df_labor_income_long %>%
  complete(
    Year = seq(min(Year) , max(Year) + 0.75, by = 0.25)
  ) %>%
  mutate(
    Quarter = as.yearqtr(Year),
  ) %>%
  arrange(Quarter) %>%
    mutate(Value = lag(Value, n = 3)) %>% 
    slice(-c(1:3))

# Interpolate values for missing quarters
df_labor_income_long$Value <- zoo::na.approx(df_labor_income_long$Value)

# Use mean growth rate of the Quarters in the dataset to approx the quarters to Q3 2024
df_labor_income_long <- df_labor_income_long %>% 
    mutate(labor_growth = log(Value / lag(df_labor_income_long$Value))) 

mean_growth_rate_labor <- mean(df_labor_income_long$labor_growth, na.rm = TRUE)

# Extrapolate the data up to 2024 Q3
value_2024_Q1 <- df_labor_income_long$Value[nrow(df_labor_income_long)] * exp(mean_growth_rate_labor)
value_2024_Q2 <- value_2024_Q1 * exp(mean_growth_rate_labor)
value_2024_Q3 <- value_2024_Q2 * exp(mean_growth_rate_labor)

# Add these values to the dataframe
df_labor_income_long <- df_labor_income_long %>% 
    add_row(Quarter = as.yearqtr("2024 Q1", format = "%Y Q%q"), Value = value_2024_Q1) %>% 
    add_row(Quarter = as.yearqtr("2024 Q2", format = "%Y Q%q"), Value = value_2024_Q2) %>% 
    add_row(Quarter = as.yearqtr("2024 Q3", format = "%Y Q%q"), Value = value_2024_Q3)


# Remove unnessary columns
df_labor_income_long <- df_labor_income_long %>% 
    dplyr::select(-Year, -labor_growth)


# Remove all rows prior to 2019 Q4 in labor income
df_labor_income_long <- df_labor_income_long %>% 
    filter(Quarter >= "2019 Q3")

# Make to log scale
df_labor_income_long <- df_labor_income_long %>% 
    mutate(Value = log(Value))

# Calculate growth rate for labor_income to the quarter 2019 Q3
df_labor_income_long <- df_labor_income_long %>% 
    mutate(labor_growth = log(Value / df_labor_income_long$Value[1])) %>% 
    slice(2:n())

# Use growth rate to calculate the labor income growth until 2024
growth_rate_labor <-  df_labor_income_long$labor_growth
additional_labor_income <- df_cay_current$y[271] * exp(growth_rate_labor)

# Add the data to the cay_current dataframe
df_cay_current[is.na(df_cay_current$y), "y"] <- additional_labor_income 


```


3. Consumption


```{r}

# Consumption data
consumption_growth_labor <- df_pce_growth %>% 
    filter(Quarter >= "2019 Q3")

# Make to log scale
consumption_growth_labor <- consumption_growth_labor %>% 
    mutate(pce_growth = log(PCE))

# Calculate the growth of the pce from the base of 2019 Q3
consumption_growth_labor <- consumption_growth_labor %>% 
    mutate(pce_growth = log(PCE / consumption_growth_labor$PCE[1])) %>% 
    slice(2:n())


# Use growth rate to calculate the consumption growth until 2024
growth_rate_consumption <-  consumption_growth_labor$pce_growth
additional_consumption <- df_cay_current$c[271] * exp(growth_rate_consumption)

# Add the data to the cay_current dataframe
df_cay_current <- df_cay_current[-nrow(df_cay_current), ]
df_cay_current[is.na(df_cay_current$c), "c"] <- additional_consumption


# Calculate the cay_tfor the missing time frame
additional_cay_t <- df_cay_current %>% 
    filter(is.na(cay_t)) %>%
    mutate(cay_t = c - 0.218 * w - 0.801 * y + 0.441) %>%
    dplyr::select(-w, -y, -c)

# Add the data to the cay_current dataframe
df_cay_current[is.na(df_cay_current$cay_t), "cay_t"] <- additional_cay_t$cay_t
```



##### 2 RREL

```{r}
# Relative T-Bill Rate

# Make the monthly data into quarterly data
df_TB3MS <- df_TB3MS %>% 
    mutate(observation_date = as.Date(observation_date)) %>% 
    group_by(Year = year(observation_date), Quarter = quarter(observation_date)) %>% 
    summarise(TB3MS = mean(TB3MS)) %>% 
    ungroup() %>% 
    mutate(Quarter = paste(Year, "Q", Quarter, sep = "")) %>% 
    dplyr::select(-Year)


# Add quarters
df_TB3MS <- df_TB3MS %>% 
    mutate(Quarter = as.yearqtr(Quarter, format = "%YQ%q")) %>% 
    rename("T_Bill_Rate" = TB3MS) %>%
    mutate(T_Bill_Rate = T_Bill_Rate / 100)


# Rolling t-bill
rrel <- df_TB3MS %>%
    arrange(Quarter) %>%
  mutate(
    T_Bill_MA = rollapply(T_Bill_Rate, width = 12, mean, align = "right", fill = NA), # 12-month MA
    RREL_t = T_Bill_Rate - T_Bill_MA  # Calculate RREL_t
  ) %>% 
    dplyr::select(-T_Bill_MA) %>% 
    filter(Quarter >= "1970 Q1") %>%
    mutate(T_Bill_Rate = T_Bill_Rate + 1)
```

##### 3 Consumption Growth

```{r}
# Consumption growth
consumption_growth <- df_PCECC96 %>% 
    mutate(Quarter = as.yearqtr(DATE, format = "%Y-%m-%d")) %>%
    dplyr::select(-DATE, PCE = PCECC96) %>% 
    filter(Quarter >= "1969 Q4") %>% 
    mutate(pce_growth = PCE / lag(PCE)) %>% 
    filter(row_number() != 1)


```



#### 5 Combine Data in different ways for the analysis 

1. All Assets

```{r}
# All assets

# Full join all Data together
df_all_assets <- bind_rows(df_equity, non_equity_HKM, r_f) %>%
    # Filter all data from 1969 Q4
    filter(Quarter >= "1969 Q4")

# Inner_join the Net worth share and aggregate leverage
df_all_assets <- df_all_assets %>% 
    inner_join(net_worth_share_long, by = "Quarter") %>% 
    rename(psi_t = Value) %>%
    inner_join(aggregate_leverage_long, by = "Quarter") %>%
    rename(phi_t = Value) %>%
    inner_join(df_cay_current, by = "Quarter") %>%
    dplyr::select(-"c", -"w", -"y") %>%
    inner_join(rrel, by = "Quarter") %>%
    inner_join(df_pce_growth, by = "Quarter") %>%
    dplyr::select(-"PCE", "consumption_growth" = "pce_growth") %>%
    # Add a column with average excess returns over T-Bill Rate
    mutate(avg_excess_return = returns - T_Bill_Rate)



# Check for NA in the all assets dataframe
print(paste("Number of NA in the all assets dataframe:", sum(is.na(df_all_assets))))

# Remove all rows that contain NA's it does not matter where those NA's are.
df_all_assets <- df_all_assets %>% 
    drop_na()




# write_csv(df_all_assets, "cleaned_data/df_all_assets.csv")
```



2. Equity

```{r}
# Equity only

# Full join all Data together
df_equity <- bind_rows(df_equity) %>%
    # Filter all data from 1970 Q1
    filter(Quarter >= "1971 Q1") %>% 
    filter(Quarter <= "2019 Q4")

# Inner_join the Net worth share and aggregate leverage
df_equity <- df_equity %>% 
    inner_join(net_worth_share_long, by = "Quarter") %>% 
    rename(psi_t = Value) %>%
    inner_join(aggregate_leverage_long, by = "Quarter") %>%
    rename(phi_t = Value) %>%
    inner_join(df_cay_current, by = "Quarter") %>%
    dplyr::select(-"c", -"w", -"y") %>%
    inner_join(rrel, by = "Quarter") %>%
    inner_join(df_pce_growth, by = "Quarter") %>%
    dplyr::select(-"PCE", "consumption_growth" = "pce_growth") %>%
    # Add a column with average excess returns over T-Bill Rate
    mutate(avg_excess_return = returns - T_Bill_Rate)


# Check for NA in the all assets dataframe
print(paste("Number of NA in the equity dataframe:", sum(is.na(df_equity))))
```



3. Non-Equity

```{r}

# Non-Equity only

# Inner_join the Net worth share and aggregate leverage
df_non_equity <- non_equity_HKM %>% 
    inner_join(net_worth_share_long, by = "Quarter") %>% 
    rename(psi_t = Value) %>%
    inner_join(aggregate_leverage_long, by = "Quarter") %>%
    rename(phi_t = Value) %>%
    inner_join(df_cay_current, by = "Quarter") %>%
    dplyr::select(-"c", -"w", -"y") %>%
    inner_join(rrel, by = "Quarter") %>%
    inner_join(df_pce_growth, by = "Quarter") %>%
    dplyr::select(-"PCE", "consumption_growth" = "pce_growth") %>%
    # Add a column with average excess returns over T-Bill Rate
    mutate(avg_excess_return = returns - T_Bill_Rate)


# Check for NA in the all assets dataframe
print(paste("Number of NA in the non-equity dataframe:", sum(is.na(df_non_equity))))
```

--------------






#### 6 Remove some varibales from the envirnonment

```{r}
rm(df_equity_monthly)
rm(df_equity_monthly_long)
rm(additional_cay_t)
rm(aggregate_leverage)
rm(df_compensation_of_employees)
rm(df_contr_social_gov)
rm(df_cpi)
rm(df_He_Kelly_Manela_Factors_And_Test_Assets)
rm(df_labor_income)
rm(df_labor_income_long)
rm(df_personal_income_other)
rm(df_personal_current_transfer)
rm(df_personal_current_taxes)
rm(aggregate_leverage_long)
rm(consumption_growth_labor)
rm(df_cay_current)
rm(df_pce_growth)
rm(df_PCECC96)
rm(df_wealth)
rm(df_wealth_growth)
rm(df_wealth_net)
rm(df_wealth_net_long)
rm(leverage_ratio_bd)
rm(leverage_ratio_bd_long)
rm(leverage_ratio_bhc)
rm(leverage_ratio_bhc_long)
rm(net_worth_share)
rm(net_worth_share_long)
rm(rrel)
rm(total_assets_bd)
rm(total_assets_bd_long)
rm(total_assets_bhc)
rm(total_liabilities_bd)
rm(total_liabilities_bd_long)
rm(total_liabilities_bhc)
rm(value_2024_Q1)
rm(value_2024_Q2)
rm(value_2024_Q3)
rm(yq)
rm(start_year_qtr)
rm(list_of_files)
rm(additional_wealth)
rm(additional_labor_income)
rm(additional_consumption)
rm(dataframe_name)
rm(end_year_qtr)
rm(growth_rate_consumption)
rm(growth_rate_labor)
rm(mean_growth_rate_labor)
rm(growth_rate_wealth)
rm(non_equity_HKM)

consumption_growth_instrument <- consumption_growth
rm(consumption_growth)
```



------------

<br>




# 3 Estimation of the HI-SDF Model

In this section, we will estimate the HI-SDF model proposed by Sa Mai (2023). 

First we will define the moment conditions and the sieve estimation of the conditional mean M(w_t).

Step 0: Simulate the data

```{r}

```




Step 1: Load data

```{r}
# Step 1: Estimate \omega Using Sieve Minimum Distance (SMD)

data <- df_equity


# Assign variables
psi <- data$psi_t
phi <- data$phi_t
returns <- data$returns # Example: asset returns
consumption_growth <- data$consumption_growth



# Extract instruments from the data (adjust column names as needed)
instruments <- as.matrix(data[, c("cay_t", "RREL_t", "avg_excess_return", "phi_t")]) 
instruments <- scale(instruments, center = rep(1, 4)) # Standardize the instruments
```


Step 2: Define initial guesses for β and γ

```{r}
# Initial guesses for β and γ
beta <- 0.98 # Time discount factor
gamma <- 15  # Risk aversion
params <- c(beta, gamma) # Combine into a vector
```




Step 3: Setup Sieve Approximation


1. Define B-splines and Tensor Product Basis Functions

```{r}
# Define knots for ψ and φ based on quantiles
knots_psi <- quantile(psi, probs = seq(0, 1, length.out = 4))
knots_phi <- quantile(phi, probs = seq(0, 1, length.out = 4))

# Generate B-spline basis functions
bs_psi <- bs(psi, knots = knots_psi, degree = 3, intercept = TRUE)
bs_phi <- bs(phi, knots = knots_phi, degree = 3, intercept = TRUE)


# Call the function
tensor_product <- compute_tensor_product(bs_psi, bs_phi)
```



2. Define the SMD Error Term using OLS

```{r}
# Define the SMD procedure for a given beta and gamma
smd_error <- function(beta, gamma, psi_t, phi_t, C_growth, returns) {
  
  # Dependent variable
  y <- (1 / beta) * (C_growth^gamma) / returns
  
  # Perform OLS
  ols_result <- lm(y ~ tensor_product - 1)  # "-1" excludes intercept since it's part of design_matrix
  
  # Compute residuals
  residuals <- resid(ols_result)
  
  # Return the total squared error
  mean(residuals^2)
}


```



3. Define the Estimate Omega Function



Then we will do the following: 
1. I will tell you the procedure as I understand it step by step.
2. You will tell me if this procedure is **exactly** in line with what Sai Ma has done in the first step profile SMD Estimation of Omega.

Let me break the Profile SMD Estimation as can be found in Sai Ma:
1. Define knots for psi and phi based on the quantiles.
2. Generate B-spline basis functions for phi and psi.
3. Generate the tensor product of the B-splines of phi and psi. 
4. Use the Sieve Least Squares approach to estimate the sieve function. This includes:
4.1. Estimate the conditional moment condition M(w_t, nu, Omega) = E[chi(z_{t+1}, nu, Omega) | w_t] consistently and nonparametrically. Where w_t are the instruments, z_{t+1} is a vector containing all observations including consumption growth, asset return, aggregate leverage and net worth share. The Sieve Least Square estimator for M_hat(w_t, nu, Omega) = (sum_{t=1}^T chi(z_{t+1}, nu, Omega) * p^(T_J)(w_t)' * (P'P)^(-1)) * p^(T_J)(w)
4.2. Minimize the weighted quadratic norm of the in step 4.1. estimated conditional expectation functions.
5. Build a grid of beta and gamma and redo step 4 for every combination of beta and gamma.
6. Choose the beta and gamma and the Omega that minimizes the weighted quadratic norm of the estimated conditional expectation functions.
7. Save the estimated Omega_hat as the initial estimate of omega for the GMM estimation of beta and gamma and the final estimate of omega.





```{r}
# Function to fit Ω(ψ, φ)
estimate_omega <- function(beta, gamma, C_growth, returns, tensor_product) {
    
    # Dependent variable calculation for Regression
    y <- (1 / beta) * (C_growth^gamma) / returns
    
    
    # Perform cross-validation for ridge regression
    cv_fit <- cv.glmnet(as.matrix(tensor_product),
                        y,
                        alpha = 0,
                        intercept = FALSE)
    
    # Extract coefficients for the optimal lambda
    coefficients <- as.numeric(coef(cv_fit, s = "lambda.min")[-1]) # Exclude intercept
    
    
    # Check the length of omega_coefficients
    cat("Length of omega_coefficients:",
        length(coefficients),
        "\n")
    cat("Number of columns in tensor_product:",
        ncol(tensor_product),
        "\n")
    
    # Check for NA values in coefficients
    if (any(is.na(coefficients))) {
        stop(
            "NA values detected in omega_coefficients. Check for multicollinearity or missing data."
        )
    }
    
    return(coefficients)
}
```



4. Define a beta-gamma-grid and search over it to find the optimal beta and gamma and to calculate my 









Step 4: GMM Estimation for β and γ and Ω(ψ, φ)

```{r}
# Compute the SDF
compute_sdf <- function(beta, gamma, consumption_growth, tensor_product, omega_coefficients) {
  # Consumption growth term
  consumption_ratio <- consumption_growth
  sdf <- beta * (consumption_ratio ^ (-gamma)) * (tensor_product %*% omega_coefficients)
  return(as.vector(sdf))
}

# Compute the residuals for GMM
compute_gmm_residuals <- function(params, consumption_growth, returns, tensor_product, omega_coefficients, instruments) {
  beta <- params[1]
  gamma <- params[2]
  
  # Compute SDF
  sdf <- compute_sdf(beta, gamma, consumption_growth, tensor_product, omega_coefficients)
  
  # Compute residuals based on Euler equation
  residuals <- (sdf * returns - 1) %*% instruments
  
  
  # Debugging: Check residual statistics
  apply(residuals, 2, summary)  # Summarize each moment
  
  
  # Normalize residuals to prevent dominance
  residuals <- residuals / max(abs(residuals))

  return(residuals)
}


# GMM objective function
gmm_objective <- function(params, consumption_growth, returns, tensor_product, omega_coefficients, instruments, ...) {

  # Compute residuals
  residuals <- compute_gmm_residuals(params, consumption_growth, returns, tensor_product, omega_coefficients, instruments)
  
  # GMM objective: Minimize the sum of squared residuals
  return(sum(residuals^2))
}

gmm_objective_debug <- function(params, consumption_growth, returns, tensor_product, omega_coefficients, instruments) {
  obj_val <- gmm_objective(params, consumption_growth, returns, tensor_product, omega_coefficients, instruments)
  cat("Objective Function Value:", obj_val, "\n")
  return(obj_val)
}

```



Step 5: Iterative Procedure

```{r}
# Tolerance and max iterations
tolerance <- 1e-8
max_iterations <- 100
iteration <- 0
converged <- FALSE

while (!converged && iteration < max_iterations) {
  iteration <- iteration + 1
  
  print(iteration)
  
  
  # Step 1: Estimate Ω(ψ, φ)
  omega_coefficients <- estimate_omega(returns, tensor_product)
  
  print(cat("Omega Coeffs for tensor product:", omega_coefficients, "\n"))
  
  # Step 2: Update β and γ using GMM
  opt <- optim(
    par = params,
    fn = gmm_objective,
    consumption_growth = consumption_growth,
    returns = returns,
    tensor_product = tensor_product,
    omega_coefficients = omega_coefficients,
    instruments = instruments,
    method = "BFGS",
  control = list(trace = 1, REPORT = 1) 
  )
  
  # Check convergence
  params_new <- opt$par
  cat("New Params (Iteration):", params_new, "\n")  # Debug line
  cat("Param Change:", max(abs(params_new - params)), "\n")
  if (max(abs(params_new - params)) < tolerance) {
    converged <- TRUE
  }
  
  params <- params_new # Update parameters
  cat("Iteration:", iteration, "Beta:", params[1], "Gamma:", params[2], "\n")
}

# Final estimates
beta_final <- params[1]
gamma_final <- params[2]
omega_final <- omega_coefficients

```




Step 6: Debug Station

```{r}
# Check dimensions
cat("Dimensions of tensor_product:", dim(tensor_product), "\n")
cat("Length of omega_coefficients:", length(omega_coefficients), "\n")

cat("Dimensions of instruments:", dim(instruments), "\n")
length((sdf * returns - 1))

sum(is.na(returns)) # Count NA values
sum(is.na(tensor_product)) # Count NA values
cor_matrix <- cor(tensor_product)
print(cor_matrix)

summary(tensor_product)
summary(returns)
max(tensor_product)
min(tensor_product)

sum(is.na(psi)) # Count NA values in psi
sum(is.na(phi)) # Count NA values in phi

sum(is.na(bs_psi)) # Count NA values in bs_psi
sum(is.na(bs_phi)) # Count NA values in bs_phi




# Compute correlation matrix
cor_matrix <- cor(tensor_product, use = "complete.obs")

# Check for high correlations
high_corr <- which(abs(cor_matrix) > 0.9, arr.ind = TRUE)
cat("Highly correlated columns (threshold > 0.9):\n", high_corr, "\n")


# Check structure of tensor_product
cat("Class of tensor_product:", class(tensor_product), "\n")
cat("Is tensor_product a matrix?:", is.matrix(tensor_product), "\n")
cat("Dimensions of tensor_product:", dim(tensor_product), "\n")

# Check structure of omega_coefficients
cat("Class of omega_coefficients:", class(omega_coefficients), "\n")
cat("Is omega_coefficients numeric?:", is.numeric(omega_coefficients), "\n")
cat("Length of omega_coefficients:", length(omega_coefficients), "\n")

gamma_values <- seq(5, 20, by = 0.5)  # Test gamma values
objective_values <- sapply(gamma_values, function(g) {
  gmm_objective(c(params[1], g), consumption_growth, returns, tensor_product, omega_coefficients, instruments)
})

plot(gamma_values, objective_values, type = "l", main = "GMM Objective Function", xlab = "Gamma", ylab = "Objective Value")


beta_values <- seq(0.5, 1.5, by = 0.05)
objective_values <- sapply(beta_values, function(g) {
  gmm_objective(c(params[2], g), consumption_growth, returns, tensor_product, omega_coefficients, instruments)
})
plot(beta_values, objective_values, type = "l", main = "GMM Objective Function", xlab = "Beta", ylab = "Objective Value")



apply(data[c("psi_t", "phi_t", "consumption_growth", "returns")], 2, sd)


summary(consumption_growth)
hist(consumption_growth, breaks = 50, main = "Distribution of Consumption Growth")

gamma_values <- seq(0, 50, by = 0.1)
objective_values <- sapply(gamma_values, function(g) {
  gmm_objective(c(params[1], g), consumption_growth, returns, tensor_product, omega_coefficients, instruments)
})

plot(gamma_values, objective_values, type = "l", main = "GMM Objective Function", xlab = "Gamma", ylab = "Objective Value")


beta_values <- seq(-5, 15, by = 0.25)
objective_values <- sapply(beta_values, function(b) {
  gmm_objective(c(b, params[2]), consumption_growth, returns, tensor_product, omega_coefficients, instruments)
})

plot(beta_values, objective_values, type = "l", main = "GMM Objective Function", xlab = "Beta", ylab = "Objective Value")

cor_matrix <- cor(tensor_product)
hist(cor_matrix[lower.tri(cor_matrix)], breaks = 50, main = "Correlation of Basis Functions")


print(summary(omega_coefficients))
plot(omega_coefficients, main = "Estimated Omega Coefficients")

summary(tensor_product)
range(tensor_product)


summary(returns)
hist(returns, breaks = 50, main = "Distribution of Returns")

print(cv_fit$lambda.min)
plot(cv_fit)


summary(coefficients)
plot(coefficients, main = "Estimated Omega Coefficients")

length(knots_psi)
length(knots_phi)



# Step 1: Fix phi_t at its mean
phi_mean <- quantile(phi, probs = 0.5)  # Calculate mean of phi_t

# Step 2: Define a range of psi_t values
psi_range <- seq(min(psi), max(psi), length.out = 100)  # Generate range of psi_t values

# Step 3: Compute B-spline basis functions for psi_t and fixed phi_t
bs_psi <- bs(psi_range, knots = knots_psi, degree = 3, intercept = TRUE)  # Basis for psi_t
bs_phi_fixed <- bs(rep(phi_mean, 100), knots = knots_phi, degree = 3, intercept = TRUE)  # Basis for phi_t

# Step 4: Compute the tensor product for the fixed phi_t
tensor_product_fixed <- apply(bs_psi, 1, function(row) {
  as.vector(outer(row, bs_phi_fixed[1, ]))  # Tensor product for each psi_t
})
tensor_product_fixed <- t(tensor_product_fixed)  # Ensure correct dimensions

# Step 5: Evaluate the omega function
omega_values <- tensor_product_fixed %*% omega_coefficients

# Step 6: Plot the omega function against psi_t
plot(psi_range, omega_values, type = "l", col = "blue", lwd = 2,
     xlab = expression(psi[t]), ylab = expression(Omega(psi[t], phi[t])),
     main = expression(paste("Omega Function with ", phi[t], " = Mean(", phi[t], ")")))



psi_mean <- mean(psi)

# Step 2: Define a range of phi_t values
phi_range <- seq(min(phi), max(phi), length.out = 100)  # Generate range of phi_t values

# Step 3: Compute B-spline basis functions for phi_t and fixed psi_t
bs_phi <- bs(phi_range, knots = knots_phi, degree = 3, intercept = TRUE)  # Basis for phi_t
bs_psi_fixed <- bs(rep(psi_mean, 100), knots = knots_psi, degree = 3, intercept = TRUE)  # Basis for psi_t

# Step 4: Compute the tensor product for the fixed psi_t
tensor_product_fixed <- apply(bs_phi, 1, function(row) {
  as.vector(outer(row, bs_psi_fixed[1, ]))  # Tensor product for each phi_t
})
tensor_product_fixed <- t(tensor_product_fixed)  # Ensure correct dimensions

# Step 5: Evaluate the omega function
omega_values <- tensor_product_fixed %*% omega_coefficients

# Step 6: Plot the omega function against phi_t
plot(phi_range, omega_values, type = "l", col = "blue", lwd = 2,
     xlab = expression(phi[t]), ylab = expression(Omega(psi[t], phi[t])),
     main = expression(paste("Omega Function with ", psi[t], " = Mean(", psi[t], ")")))


quantile(psi)
quantile(log(phi))
exp(3)


beta_values <- seq(0.5, 2, length.out = 20)
gamma_values <- seq(0.5, 50, length.out = 20)

objective_values <- outer(beta_values, gamma_values, Vectorize(function(beta, gamma) {
  gmm_objective(c(beta, gamma), consumption_growth, returns, tensor_product, omega_coefficients, instruments)
}))


plot_ly(x = beta_values, y = gamma_values, z = objective_values) %>%
    add_surface() %>%
    layout(
        title = "Reconstructed Omega(psi, phi)",
        scene = list(
            xaxis = list(title = "beta"),
            yaxis = list(title = "gamma"),
            zaxis = list(title = "objective")
        )
    )



apply(instruments, 2, summary)  # Summarize each instrument

cor_psi <- cor(data$psi_t, instruments)
cor_phi <- cor(data$phi_t, instruments)


cat("Correlation with Psi:", cor_psi, "\n")
cat("Correlation with Phi:", cor_phi, "\n")


```












# Fama Macbeth regression

```{r}
## Step 3: Compute Risk Prices Using Linear Model

# Compute \beta_j,c and \beta_j,\Omega for each asset
betas <- lapply(split(df_all_assets, df_all_assets$asset_id), function(asset_data) {
    # Time-series regression for each asset
    fit <- lm(returns ~ consumption_growth + log(tensor_product %*% omega_coefficients), data = df_all_assets)
    return(coef(fit))  # Return coefficients (factor loadings)
})
betas <- do.call(rbind, betas)  # Combine results for all assets into a matrix or data frame
colnames(betas) <- c("(Intercept)", "consumption_growth", "log(omega_estimated_gmm)")  # Ensure proper column names

# Prepare a data frame for cross-sectional regression
cross_sectional_data <- data.frame(
    avg_excess_return = tapply(df_all_assets$avg_excess_return, df_all_assets$asset_id, mean),
    consumption_growth_beta = betas[, "consumption_growth"],
    omega_beta = betas[, "log(omega_estimated_gmm)"]
)

# Cross-sectional regression for risk prices
cross_sectional_fit <- lm(avg_excess_return ~ consumption_growth_beta + omega_beta, data = cross_sectional_data)

# Extract risk prices
lambda_c <- coef(cross_sectional_fit)["consumption_growth_beta"]  # Risk price of consumption growth
lambda_omega <- coef(cross_sectional_fit)["omega_beta"]  # Risk price of \Omega

## Results
cat("Risk price of consumption growth (lambda_c):", lambda_c, "\n")  # Output \lambda_c
cat("Risk price of omega (lambda_omega):", lambda_omega, "\n")  # Output \lambda_\Omega
```



# Expected Return-Beta Representation
```{r}
# Step 6: Compute Expected Return-Beta Representation
# Load necessary libraries




```











